Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-07-12 Response.tex

\item 
    \begin{itshape}
Is this method exceptionally difficult to adapt to create a numerical example from LEO or GTO?  These would be the most pragmatically interesting departure orbits to the mission design community.  Section 6.2 presents an example from GEO, but it is unlikely that GEO represents a "typical" parking orbit, since there is no reason to insert a spacecraft into GEO before it transfers to the destination orbit.  This should be called out in the conclusions or future work.
\end{itshape}

This method is not difficult to adapt for other scenarios.
However, there is a certain amount of experimentation to ensure that trajectories converge. 
In addition, the details in this paper were designed in the context of the planar three body problem and as a result and extension to the nonplanar GTO is non trivial.
The examples presented are primarily aimed at introducing and demonstrating the feasibility of this approach, rather than designing operational mission profiles for spacecraft.
However, this is a valuable comment and a goal of future research. 
Additional detail has been included in the conclusion discussing this topic.

### 2017-07-13 Response.tex

\subsection*{Reviewer 1} 
\begin{itshape}
Reviewer \#1: I have some issues with this paper that, in my opinion necessitate a major revision.
These issues are:
\end{itshape}

\begin{itemize}
    \item 
        \begin{itshape}
-It extensively re-covers issues that have been covered in many papers, making it difficult to disseminate what the original contributions are.  For example, I don't think the addition of the thrust term into the dynamics necessitates re-doing every piece of analysis that has been done with various resources in the literature about variational integrators (including comparisons with RK methods).  Things that can be found in other research should be cited, and summary comments can be used to point the readers to fill in this knowledge.  The content of this paper easily be reduced considerably to maintain focus on the original contributions.
    \end{itshape}

    The paper is being reduced. 
    The introduction has been reduced to avoid excessive repetition. 
    In addition, much of the background material has been removed

\item
    \begin{itshape}
-It does not give a complete picture of the pros and cons of the proposed methodology.  This method is full of both advantages and disadvantages.  I don't think the authors need to be concerned with "selling" the work to the community, but rather showing the full and honest picture given the current state of the research.  In the conclusions, the potential cons to this research can be mitigated by setting a path forward for future research to further improve the methodology.

@@

These pros/cons include:

-The formulation of the problem with acceleration magnitude is a major technical challenge for mission design practitioners.  The state of the art to design trajectories that depend on low-thrust engine hardware is either:

-To produce constant thrust magnitude or no thrust magnitude (typical of nuclear electric propulsion, or very simple electric propulsion systems.)

-To produce variable thrust magnitude associated with various throttle points at different power accessibility levels (solar electric propulsion).
That is not to say that useful solutions cannot be extracted from the problem, as the authors have shown.  However, a great many solutions in this approach will be unusable due to the fact that acceleration and thrust magnitude are different, i.e. a=T/m

Thus - a MAJOR focus of future work should be the introduction of a seventh state (mass).  This gives rise to a more challenging optimal control problem requiring the switching function, but it is the form that is generally needed in computing optimal open-loop trajectories that can actually be flown.
\end{itshape}

\item 
    \begin{itshape}
The pros and cons of the PCRTBP

-The PCRTB gives rise to exploiting Poincare sections in a systematic manner.  2D solutions might be close enough for qualitative understanding of the solution space for many problems (as long as large plane changes aren't needed).

-The PCRTB is limiting for many pragmatic departure orbits (e.g. LEO and GTO, the most common departure orbits for low-thrust transfers).
\end{itshape}

@@

Additional detail has been included in the problem formulation section.
This includes some discussion on the choice of the PCRTBP and the relative strengths/weaknesses of this approach.
The additional paragraph has been copied below.

\begin{correction}
We utilize the planar circular restricted three body problem~(PCRTBP) as the basis of our system definition. 
It is a popular model in the preliminary analysis of multibody spacecraft trajectories. 
In the context of Earth based mission, the PCRTBP affords a relatively simple dynamic model while still capturing the major third body perturbation of the Moon.
In addition, this model allows for a systematic process to define and exploit \Poincare sections.
Furthermore, the 2D solutions afforded by the PCRTBP are frequently use to gain a qualitative understanding of the trade space of transfers in the Earth-Moon system.
The PCRTBP approach offers insight into the fundamental dynamical structure while capturing the major dynamic properties of the planar motion.
As a result, this approach is best suited for trajectories which do not require large plane changes.
\end{correction}

\item 
    \begin{itshape}
The pros and cons of variational integrators should really be acknowledged rather than completely dismissing the RK methods which are still the current state of the art in mission design (using higher-orders and suitable tolerances)

-Pros = boundedness in the energy behavior.  Very long term integration will not deviate from the known dynamical structure.

-Cons = you don't know where you are on the energy surface, just that you are on it somewhere.  This is still a problem in actual trajectory design.  Knowing the error is on an energy surface does not mean that you don't have error.
\end{itshape}
\end{itemize}
From here on out comments specific to various sections of the paper follow:

@@

\item 
    \begin{itshape}
Is this method exceptionally difficult to adapt to create a numerical example from LEO or GTO?  These would be the most pragmatically interesting departure orbits to the mission design community.  Section 6.2 presents an example from GEO, but it is unlikely that GEO represents a "typical" parking orbit, since there is no reason to insert a spacecraft into GEO before it transfers to the destination orbit.  This should be called out in the conclusions or future work.
\end{itshape}

This method is not difficult to adapt for other scenarios.
However, there is a certain amount of experimentation to ensure that trajectories converge. 
In addition, the details in this paper were designed in the context of the planar three body problem and as a result and extension to the nonplanar GTO is non trivial.
The examples presented are primarily aimed at introducing and demonstrating the feasibility of this approach, rather than designing operational mission profiles for spacecraft.
However, this is a valuable comment and a goal of future research. 
Additional detail has been included in the conclusion discussing this topic.

\item 
    \begin{itshape}
The authors should discuss some statistics of the convergence of their multiple shooting TPBVP - number of iterations, compute time, etc.
\end{itshape}

Most of the literature tends to not spend time discussing the low level details of the computational procedure, e.g.~\cite{grebow2011,stuart2010}.
In addition, the number of iterations, computation time and even the eventual cost function value are highly dependent on the specific system and more specifically the implementation of the algorithm in software. 
There are a wide variety of works which are focused more exclusively on the computational implementation of various optimal control techniques which do spend significant time on the computational characteristics.
However, our manuscript is primarily focused on demonstrating the feasbility of using reachability sets to design transfer trajectories.
As a result, there is not much benefit to detailed statistics of the implementation of this methodology.

@@

\item 
    \begin{itshape}
Can any intuition be gained from reporting the optimal converged cost function values in section 6.1 and 6.2?  One could at least compare them to compare the reachability in the two different examples.
\end{itshape}

The cost function only parameterizes the distance between the controlled and uncontrolled terminal states on the \Poincare section. 
In addition, each state which lies on the reachable set would typically have a different distance and therefore a different coverged cost function value. 
Furthermore, it would be difficult to characterize a single parameter which characterizes the reachable set, in the form of the cost function, for all states of the reachable set. 
Also, the cost function is highly dependent on the transit time of trajectory, i.e. a longer transit time corresponds to a larger reachable set and a larger magnitude of the cost function.
However, this is an interesting suggestions for future research.
For example, the cost function gives some indication of area/volume of the reachable set. 
It may be possible to use this value as another way to characterize the subspace on the \Poincare section and is an intriguing avenue of future research.

@@

Parker, J. and Anderson, R., "Low-Energy Lunar Trajectory Design," DEEP SPACE COMMUNICATIONS AND NAVIGATION SERIES, Jet Propulsion Laboratory Pasadena, California, July 2013.

Online Copy: https://descanso.jpl.nasa.gov/monograph/series12/LunarTraj--Overall.pdf
\end{itshape}

\item 
    \begin{itshape}
For what it's worth, exploiting sun perturbations with low-thrust in the Earth-moon RTBP would be highly beneficial and represent a worthy avenue of future research (more on this below.)
\end{itshape}

This is a very useful and interesting suggestion and something that we will take into consideration for future research.

\item 
    \begin{itshape}
The conclusions of the paper should acknowledge other potentially limiting factors of the presented analysis

-Omits advantage of exploiting fourth body perturbation (Sun in Earth/moon RTBP)

-Transfers are 2D only, method is more challenging to adapt to 3D

-Presented control magnitudes are dimensionally large, and more work is needed to determine feasibility of approach for lower accelerations

-Thrust and mass are completely decoupled from the analysis, which is limiting in terms of finding suitable hardware that can deliver the controls needed, as currently presented.
\end{itshape}

### 2017-07-13 Response.tex

\item
    \begin{itshape}
"Low energy transfers from the Earth to the Lagrange points are necessary for future missions."  One must be careful not to confuse these with traditional "low-energy transfers" to the moon, which use Sun third-body perturbations to transfer into lunar orbit.  These are what many mission designers define as "low-energy" lunar transfers.  This is actually a four-body problem (Sun, Earth, moon, spacecraft), and represents additional delta-V savings (as was done with NASA's GRAIL mission.)

Example:

Parker, J. and Anderson, R., "Low-Energy Lunar Trajectory Design," DEEP SPACE COMMUNICATIONS AND NAVIGATION SERIES, Jet Propulsion Laboratory Pasadena, California, July 2013.

Online Copy: https://descanso.jpl.nasa.gov/monograph/series12/LunarTraj--Overall.pdf
\end{itshape}
This sentence has been modified to make it more clear that we're discussing low thrust propulsion rather than low-energy transfers.
The modified sentence is copied below.

\begin{correction}
Transfers from the Earth to the Lagrange points, through the use of low-thrust electric propulsion, offer an additional and potentially shorter time of flight in comparison to the low-energy transfers which utilize solar perturbations.
\end{correction}

### 2017-07-13 manuscript.tex
Differentiate between low thrust and low energy
Reviewer 1 Comment 36

% motivation - may need to compute several reachability sets
There are many situations where a more complicated and extensive orbital transfer is desired. 
For example, we present a simulation of transferring from a geostationary orbit to the a periodic orbit about the Moon.
This type of low energy transfer would be most suitable for unmanned spacecraft transitioning from the Earth to the Moon.
The long time of flight would make such a transfer unsuitable for manned missions due to life support constraints.
%This type of low energy transfer is best suited for autonomous spacecraft missions as the long time of flight is undesirable for manned spacecraft. 
Future proposals for permanent lunar spacecraft and bases will require frequent supply missions to remain viable. 
Low energy transfers from the Earth to the Lagrange points are necessary for future missions.

>>>>

% motivation - may need to compute several reachability sets
There are many situations where a more complicated and extensive orbital transfer is desired. 
For example, we present a simulation of transferring from a geostationary orbit to the a periodic orbit about the Moon.
This type of low energy transfer would be most suitable for unmanned spacecraft transitioning from the Earth to the Moon.
The long time of flight would make such a transfer unsuitable for manned missions due to life support constraints.
%This type of low energy transfer is best suited for autonomous spacecraft missions as the long time of flight is undesirable for manned spacecraft. 
Future proposals for permanent lunar spacecraft and bases will require frequent supply missions to remain viable. 
Transfers from the Earth to the Lagrange points, through the use of low-thrust electric propulsion, offer an additional and potentially shorter time of flight in comparison to the low-energy transfers which utilize solar perturbations.
